INTELLIGENT SYSTEMS

### 2021-04-08 paper_5.tex
working on 5.4.4

    \item \emph{Single task with individuals sensors} (1 Task - 1 Sensor): being a multi-task 
    network, a CNN network is created for each sensor in combination 
    with each label. As there are three types of labels and two sensors, a 
    total of 6 CNN networks are trained. From the results obtained from 
    the experiment, it can be seen that both sensors affect the model in an 
    almost similar way, in terms of accuracy and F1-Measure. These values 
    indicate that both sensors can be used in order to achive the purpose 
    of identifying the walk.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
                SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task - 1 Sensor).}
        \label{table accuracy and F1 (1 Task - 1 Sensor)}
    \end{table}

    \item \emph{Multi-task with individual sensors} (+ Task - 1 Sensor): in this experiment 
    more tasks are assigned to each of the sensors (3 tasks for 1 
    sensor) implying the creation of two CNN networks. This experiment 
    is useful to see if there are any performance improvements with respect 
    to the single assignment (defined in the previous point). The loss function 
    is that described in equation \ref{loss-function}. Comparing the results obtained 
    in table \ref{table accuracy and F1 (1 Task - 1 Sensor)} with table \ref{table accuracy and F1 (more Task - 1 Sensor)}, it can be seen that the following experiment led 
    to a slight improvement in performance.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
                MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (+ Task - 1 Sensor).}
        \label{table accuracy and F1 (more Task - 1 Sensor)}
    \end{table}

@@

\end{enumerate}

>>>>

    \item \emph{Single task with individuals sensors} (1 Task, 1 Sensor): being a multi-task 
    network, a CNN network is created for each sensor in combination 
    with each label. As there are three types of labels and two sensors, a 
    total of 6 CNN networks are trained. From the results obtained from 
    the experiment, it can be seen that both sensors affect the model in an 
    almost similar way, in terms of accuracy and F1-Measure. These values 
    indicate that both sensors can be used in order to achive the purpose 
    of identifying the walk.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
                SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, 1 Sensor).}
        \label{table accuracy and F1 (1 Task - 1 Sensor)}
    \end{table}

    \item \emph{Multi-task with individual sensors} (+ Task, 1 Sensor): in this experiment 
    more tasks are assigned to each of the sensors (3 tasks for 1 
    sensor) implying the creation of two CNN networks. This experiment 
    is useful to see if there are any performance improvements with respect 
    to the single assignment (defined in the previous point). The loss function 
    is that described in equation \ref{loss-function}. Comparing the results obtained 
    in table \ref{table accuracy and F1 (1 Task - 1 Sensor)} with table \ref{table accuracy and F1 (more Task - 1 Sensor)}, it can be seen that the following experiment led 
    to a slight improvement in performance.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
                MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (+ Task, 1 Sensor).}
        \label{table accuracy and F1 (more Task - 1 Sensor)}
    \end{table}

@@

    \item \emph{Single Task with Fusion} (1 Task, + Sensor): in this experiment 3 CNNs 
    are used, one for each task, each making up a branch. In this case, the 
    combination of data from different sensors will be useful to be able to 
    determine only 1 task and therefore only one class. The results obtained 
    are better than the previous points, except for the gender class where 
    the MultiTask approach achieves a better score.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (1 Task, + Sensor)}
    \end{table}
\end{enumerate}
